\subsubsection{{\tt fc2estuary} package}

The {\tt fc2estuary} package was developed to manage flood control
releases from a canal where the inlet is connected to reservoir with
potentially large flood control releases (e.g., Lake Okeechobee), the
outlet is connected to an estuary, and the canal receives runoff from
adjacent basins.  The assessor executes the flood control assessor for
upstream water control unit (Lake Okeechobee) and retrieves flood
control release computed for the inlet to the canal.  The assessor
compares this value to the runoff from the adjacent basins, and uses
the bigger value to set the maximum release to the estuary.
Typically, this value is used by a Regional Manager or LP Supervisor
to set a management constraint for flood control on the outlet to the
estuary.


\subsubsection{{\tt fc2estuary\_alt1} package}

The {\tt fc2estuary\_alt1} package was developed to manage flood
control releases from a canal where the inlet is connected to
reservoir with potentially large flood control releases (e.g., Lake
Okeechobee), the outlet is connected to an estuary, and the canal
receives runoff from adjacent basins.  The assessor executes the flood
control assessor for upstream water control unit (Lake Okeechobee) and
retrieves flood control release computed for the inlet to the canal.
The {\tt fc2estuary\_alt1} package compares the basin runoff with the
Lake regulatory release, and returns the larger value only when the
Lake is making a pulse release or a base flow.  Otherwise, {\tt
  fc2estuary\_alt1} returns the sum of basin runoff and Lake
regulatory release.  Typically, the return value is used by a Regional
Manager or LP Supervisor to set a management constraint for flood
control on the outlet to the estuary.  

\subsubsection{{\tt fc2estuary\_alt2} package}

The {\tt fc2estuary\_alt2} package was developed to manage flood
control releases from a canal where the inlet is connected to
reservoir with potentially large flood control releases (e.g., Lake
Okeechobee), the outlet is connected to an estuary, and the canal
receives runoff from adjacent basins.  The assessor executes the flood
control assessor for upstream water control unit (Lake Okeechobee) and
retrieves flood control release computed for the inlet to the canal.
The {\tt fc2estuary\_alt2} package compares the basin runoff with the
Lake regulatory release, and returns the larger value for any Lake
regulatory release, including base flows, pulse release and standard
regulatory releases.  Typically, the return value is used by a
Regional Manager or LP Supervisor to set a management constraint for
flood control on the outlet to the estuary.  
