\subsection{{\tt irl} package} \label{irlpackagefc}

Flood control assessment for an Indian River Lagoon (IRL) Basin can be
simulated using the {\tt irl} package. The {\tt irl} package manages
interactions between the basin and a multipurpose reservoir, optional
inlet STA, and an optional alternative outlet structure.  This flood
control assessor is intended to be paired with a {\tt irl} assessor
for water supply (see Section \ref{irlpackagews}).

The {\tt irl} package uses the following procedure to assess the flood
control needs in an IRL basin:

\begin{enumerate}

 \item Compute excess volume, defined as the portion of storage above
   the WCU's fcLevel.

 \item Compute deficit volume, defined as the portion of storage below
   the WCU's maintLevel.

 \item Compute excess flow in the basin using the following terms:
   excess and deficit volumes; basin runoff (defined as the sum of WCU
   boundary condition flows); flood control release from optional STA;
   and environmental demand release to downstream estuary;

 \item Redirect excess flow to offset environmental deficit to the
   estuary.

 \item Redirect excess flow to offset water supply releases from reservoir.

 \item Route remaining excess flow to the reservoir, subject to
   capacity, management and storage constraints.

 \item Route remaining excess flow to optional alternative outlet,
   subject to capacity and management constraints.

 \item Route remaining excess to the estuary, subject to capacity and
   management constraints.

\end{enumerate}

