\subsection{{\tt irl} package } \label{irlpackagews}

Water supply assessment in the Indian River Lagoon (IRL) basins can be
simulated using the {\tt irl} package.  The {\tt irl} package
simulates the basin interaction with a reservoir, an optional upstream
basin and a downstream estuary basin.  The {\tt irl} water supply
package is intended to be paired with a {\tt irl} assessor for flood
control (see Section \ref{irlpackagefc}).

The {\tt irl} package uses the following procedure to assess the water
supply needs for an IRL basin:

\begin{enumerate}

 \item Set basin water supply requirement to the predefined time
   series for agricultural demand and set flow for the designated
   demand outlet node.

 \item Set environmental target to the minFlow constraint placed on
   the estuary outlet.

 \item Compute basin runoff, defined as the sum of the basin boundary
   conditions flows.

 \item Compute net demand for basin (basin demand + environmental
   demand - basin runoff).

 \item Use reservoir to meet net basin demand, subject to capacity and
   management constraints, reservoir supply (volume above specified
   reserve level). Reservoir can be either multipurpose or
   agricultural only, depending on the purpose specification for the
   reservoir pump.

 \item Compute reductions to agricultural and estuary deliveries due
   to limited water supply.  Reductions are prorated, based on the
   agricultural to estuary demand ratio.

 \item Set water supply requirement for the estuary outlet and adjust
   release at the demand nodes to compensate for reductions in water
   supply delivery.

\end{enumerate}

Runoff from the optional upstream basin is not routed by the water
supply assessor.  The upstream basin runoff is added to basin excess
and routed by the {\tt irl} assessor for flood control.  

