\subsection{{\tt losaenv} package }\label{losaenvWS}

Water supply assessment in the Lake Okeechobee Service Area (LOSA)
basin that is upstream of an estuary basin can be simulated using the
{\tt losaenv} package.  These basins have agricultural water supply
requirement and are not connected to an upstream source, i.e., they do
NOT have a direct connection to Lake Okeechobee.  Runoff from the
basin can be used to meet environmental demand in the downstream
estuary.  This water supply assessor is intended to be paired with a
{\tt losaenv} assessor for flood control (see
Section \ref{losaenvFC}).

The {\tt losaenv} package uses the following procedure to manage a
basin for water supply:

\begin{enumerate}

 \item Set basin water supply requirement to predefined time series
 for agricultural demand and set flow for the designated demand outlet
 node.  By default this water supply requirement is designated as an
 ``ag'' landscape.

 \item Set environmental water supply requirement using the minFlow
 constraint placed on the estuary outlet.  By default this water
 supply requirement is designated as an ``envTarg'' landscape.

 \item Compute basin runoff, defined as the sum of the basin boundary
   conditions flows.

 \item Compute net demand for basin (basin demand + environmental
 demand - basin runoff).

 \item Compute reductions to agricultural and estuary deliveries due
   to limited water supply (i.e., not enough runoff).  Reductions are
   prorated, based on the agricultural to estuary demand ratio.

 \item Set water supply requirement for the estuary outlet and adjust
   release at the demand nodes to compensate for insufficient water
   supply delivery.

\end{enumerate}

